On Secure Delegation of SampBQP with a Classical Client

### 2020-03-23 blind.tex
Try introing blind compiler

\section{Blindness for $\QPIP_0$ protocols}
\label{sec:BlindBQP2}

@@

\def\blind{\mathsf{blind}}
\nc{\Piblind}{\ensuremath{\Pi_\blind}}
\nc{\Vblind}{\ensuremath{V_\blind}}
\nc{\Pblind}{\ensuremath{P_\blind}}
\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
\def\Pstar{P^*}
\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}

In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
\Ethan{Talk about the compiler first, and BQP after.}
We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
Generally one can obtain blindness by running a protocol under homomorphic encryption. \Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
\Ethan{Talk about FBQP too}

\nc{\ctx}[3]{\ensuremath{{{\widehat{#1}}_{#2}^{(#3)}}}}

@@

\Ethan{Too bottom-up. Need to tell more story.}
We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
First, when the plaintext is classical, the encryption can be performed classically.
Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.

@@

We start with a general form of the protocols that we'll compile.

>>>>

\section{Achieving Blindness on $\QPIP_0$ protocols}
\label{sec:BlindBQP2}

@@

\def\blind{\mathsf{blind}}
\nc{\Piblind}{\ensuremath{\Pi_\blind}}
\nc{\Vblind}{\ensuremath{V_\blind}}
\nc{\Pblind}{\ensuremath{P_\blind}}
\nc{\Pblindstar}{\ensuremath{P_\blind^*}}
\nc{\cVblind}[1]{\ensuremath{\cV_{\blind,#1}}}
\nc{\cPblind}[1]{\ensuremath{\cP_{\blind,#1}}}
\def\Pstar{P^*}
\nc{\cPstar}[1]{\ensuremath{\cP^*_{#1}}}
\nc{\ctx}[3]{\ensuremath{{{\widehat{#1}}_{#2}^{(#3)}}}}

Here we present our compiler on $\QPIP_0$ protocols that can be used to achieves blindness.
The high level idea is to run the protocol under homomorphic encryption.
Similar idea has happened in
\Ethan{TODO cite thesis} \Ethan{TODO maybe find out more about that ``simulate-able" thing in that thesis and explain the difference in the contexts}.
As we have the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
Compiling it would be a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.

We have a classical client and a quantum server.
We choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.
More precisely, when the corresponding plaintext is classical, encryption and decryption can be performed classically.
Furthermore, we notice that a ciphertext can be split into registers as with the corresponding plaintext.

A naive approach is to encrypt the initial input,
evaluate the entire protocol homomorphically,
then decode the output at the very end.
However, it is difficult to prove the soundness because... \Ethan{TODO why?}
So instead we let the verifier decrypt every round.
Then, in order the preserve blindness, the verifier generates a new set of keys for every message it sends to the prover...
Which results in the following protocol.

@@

\Ethan{Too bottom-up. Need to tell more story.}
We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.

@@
